Assessment and optimization of respiratory syncytial virus prophylaxis regimens in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}

### 2020-07-20 RSVOptimization.rnw
Generate rtf output for AAP Pediatrics
First-page abstract for medrxiv
Preprint watermark
Abstract reformatting

\documentclass[10pt,letter]{article}
\usepackage{verbatim}
\usepackage{float}
\floatplacement{figure}{H}

\usepackage[toc,page]{appendix}
\renewcommand{\appendixpagename}{Supplements}
\renewcommand{\appendixname}{Supplements}

\usepackage{printlen}
\usepackage{textcomp}
\usepackage{setspace}

\usepackage[hidelinks]{hyperref}
\usepackage[svgnames]{xcolor} % Must go before tikz and before structure.tex
\usepackage{tikz}
\usepackage{draftwatermark}
\SetWatermarkScale{1}
\SetWatermarkAngle{45}
\SetWatermarkFontSize{4ex}
\SetWatermarkHorCenter{12ex}
\SetWatermarkVerCenter{12ex}
\SetWatermarkLightness{.5}
\SetWatermarkText{DRAFT 3}

\input{paper/structure.tex}
\usepackage{amssymb}
\usepackage{wasysym}

\usepackage[bf,medium,raggedright,compact]{titlesec}
\titleformat{\section}{\normalfont\large\bfseries\scshape}{\thesection}{1em}{}
\titleformat{\subsection}{\normalfont\normalsize\bfseries}{}{0em}{}
\setcounter{secnumdepth}{3}

\usepackage{hanging}
\usepackage{graphicx}

\newlength\abstractindent
\setlength\abstractindent{1in}
\newcommand{\abstractsection}[1]{\hangpara{\abstractindent}{1}\makebox[1in][l]{\textbf{\textsc{#1}}}}
\newcommand{\abstractpara}{\hskip\abstractindent\hskip\baseparindent}

\renewcommand*{\thefootnote}{\fnsymbol{footnote}}
\renewenvironment{knitrout}{\expandafter\comment}{\expandafter\endcomment}

<<options, echo=FALSE>>=
    knitr::opts_chunk$set(echo=FALSE, message=FALSE, error=FALSE)
@

@@

<<figures, child='paper/figures.Rnw'>>=
@

@@

\section*{\centerline{Abstract}}
\begin{hangparas}{\abstractindent}{1}
\begin{onehalfspacing}

\abstractsection{Background}Respiratory syncytial virus (RSV) causes seasonal respiratory infection, with hospitalization rates of up to 50\% in high-risk infants. Palivizumab provides safe and effective, yet costly, immunoprophylaxis. The American Academy of Pediatrics (AAP) recommends palivizumab only for high-risk infants and only during the RSV season. Outside of Florida, the current guidelines do not recommend regional adjustments to the timing of the immunoprophylaxis regimen. We investigate the benefits of adjusting the RSV prophylaxis regimen in Connecticut based on spatial variation in the timing of RSV incidence.

\abstractsection{Methods}We obtained weekly RSV-associated hospital admissions by ZIP-code in Connecticut between \Sexpr{formatMonth(startDate)} and \Sexpr{formatMonth(endDate)}. We estimated the fraction of all RSV cases in Connecticut occurring during the period of protection offered by RSV immunoprophylaxis (``preventable fraction'') under the AAP guidelines. We then used the same model to estimate protection conferred by immunoprophylaxis regimens with alternate start dates, but unchanged duration.

\abstractsection{Results}The fraction of RSV hospitalizations preventable by the AAP guidelines varies by county because of variations in epidemic timing. Prophylaxis regimens adjusted for state- or county-level  variation in the timing of RSV seasons are modestly superior to the AAP-recommended regimen. The best alternative strategy yielded a preventable fraction of \Sexpr{regionStrategyCoverage("all", "countyMiddle", 1)} (\Sexpr{regionStrategyCoverageCI("all", "countyMiddle", 1, level)}), compared to \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) for the AAP recommendation.

\abstractsection{Conclusion}Initiating RSV prophylaxis based on state-level data may improve protection compared with the standard AAP recommendations. In Connecticut, county-level recommendations would provide only a modest additional benefit while adding complexity.

\abstractpara{}

\end{onehalfspacing}
\end{hangparas}

>>>>

\documentclass[10pt,letter]{article}
%%% end knitr preamble

% Do some things differently depending on which variant we're compiling
\input{paper/preamble.tex}

%%% begin knitr output
<<options, echo=FALSE>>=
    knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
@

@@

<<figures, child='paper/figures.Rnw'>>=
@
%%% end knitr output

@@

\section*{\centerline{Abstract}}
\begin{onehalfspacing}

\abstractsection{Background and Objectives} Respiratory syncytial virus (RSV) causes seasonal respiratory infection, with hospitalization rates of up to 50\% in high-risk infants. Palivizumab provides safe and effective, yet costly, immunoprophylaxis. The American Academy of Pediatrics (AAP) recommends palivizumab only for high-risk infants and only during the RSV season. Outside of Florida, the current guidelines do not recommend regional adjustments to the timing of the immunoprophylaxis regimen. We investigate the benefits of adjusting the RSV prophylaxis regimen in Connecticut based on spatial variation in the timing of RSV incidence.

\abstractsection{Methods} We obtained weekly RSV-associated hospital admissions by ZIP-code in Connecticut between \Sexpr{formatMonth(startDate)} and \Sexpr{formatMonth(endDate)}. We estimated the fraction of all RSV cases in Connecticut occurring during the period of protection offered by RSV immunoprophylaxis (``preventable fraction'') under the AAP guidelines. We then used the same model to estimate protection conferred by immunoprophylaxis regimens with alternate start dates, but unchanged duration.

\abstractsection{Results} The fraction of RSV hospitalizations preventable by the AAP guidelines varies by county because of variations in epidemic timing. Prophylaxis regimens adjusted for state- or county-level  variation in the timing of RSV seasons are modestly superior to the AAP-recommended regimen. The best alternative strategy yielded a preventable fraction of \Sexpr{regionStrategyCoverage("all", "countyMiddle", 1)} (\Sexpr{regionStrategyCoverageCI("all", "countyMiddle", 1, level)}), compared to \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) for the AAP recommendation.

\abstractsection{Conclusions} Initiating RSV prophylaxis based on state-level data may improve protection compared with the standard AAP recommendations. In Connecticut, county-level recommendations would provide only a modest additional benefit while adding complexity.

\end{onehalfspacing}
